---
title: "lab3"
author: "Yiping Li"
output: github_document
date: "`r Sys.Date()`" 
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
if(!require(leaflet)){
  install.packages("leaflet")
  library(leaflet)
}

webshot::install_phantomjs()
```

##1. Read in the data
First download and then read in with data.table:fread()

```{r}
#check if file exists: the "if (){}" function, if not exist it will be downladed

if (!file.exists("met_all.gz"))
{
download.file("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz", "met_all.gz", method="libcurl", timeout = 60)
}

met <- data.table::fread("met_all.gz")
```

##2. Check the dimensions, headers, footers. How many columns, rows are there?
```{r}
dim(met)

head(met)

tail(met)
```

##3. Take a look at the variables.
```{r}
str(met)
```

##4. Take a closer look at the key variables.
```{r}
table(met$year)
table(met$day)
table(met$hour)
summary(met$temp)
summary(met$elev)
summary(met$wind.sp)

#After checking the data we should make the appropriate modifications. Replace elevations with 9999 as NA.
met[met$elev==9999.0] <- NA
summary(met$elev)

#We also have the issue of the minimum temperature being -40C, so we should remove those observations.
met <- met[temp>-40]
met2 <- met[order(temp)]
head(met2)
```

##5. Check the data against an external data source.
```{r}
met <- met[temp>-15]
met2 <- met[order(temp)]
head(met2)
```


##6. Calculate summary statistics
```{r}
elev <- met[elev==max(elev)]
summary(elev)

met[elev==max(elev,na.rm=TRUE), .(
  temp_wind = cor(temp,wind.sp, use="complete"),
  temp_hour = cor(temp,hour,use="complete"),
  wind.sp_day=cor(wind.sp, day, use="complete"),
  wind.sp_hour=cor(wind.sp, hour,use="complete")
 )]
#this coutput should give the same as the output below

cor(elev$temp, elev$wind.sp, use="complete")
cor(elev$temp, elev$hour, use="complete")
cor(elev$wind.sp, elev$day, use="complete")
cor(elev$wind.sp, elev$hour, use="complete")
cor(elev$temp, elev$day, use="complete")
```


##7. Exploratory graphs
```{r}
hist(met$elev, breaks=100)
hist(met$temp)
hist(met$wind.sp)

library(leaflet)
leaflet(elev) %>%
  addProviderTiles('OpenStreetMap') %>% 
  addCircles(lat=~lat,lng=~lon, opacity=1, fillOpacity=1, radius=100)

library(lubridate)
elev$date <- with(elev, ymd_h(paste(year, month, day, hour, sep= ' ')))
summary(elev$date)

elev <- elev[order(date)]
head(elev)

plot(elev$date, elev$temp, type='l')
plot(elev$date, elev$wind.sp, type='l')
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
